### 2020-04-29 final_report/methodology.tex
replace model class with model family

In the decoupled sampling approach that is further described
in~\cref{sec:supervised}, we first gather a sufficiently large
training set of samples $\mathcal{T}=\left\{\left( x^{(i)},f\left(x^{(i)}\right) \right)\right\}_{i=1}^N$
to describe the behaviour of $f(x)$ across its domain.
Depending on specific model class and appropriate choice of its
hyperparameters, surrogate models $\hat{f}(x)$ are trained to minimise
the empirical risk~$R_{\text{emp.}}$ with respect to $\mathcal{T}$ and a model-specific
loss function $\mathcal{L}$, where the empirical risk is defined as
$R_{\text{emp.}}(\hat{f}\mid\mathcal{T},\mathcal{L})
	=\frac{1}{N}\sum_{i=1}^N
	\mathcal{L}\left(\hat{f}(x^{(i)}),f(x^{(i)})\right)$.

@@

Aiming to provide objective comparison of a diverse set of surrogate model
classes, we define a multitude of metrics to be tracked during experiments.
Following the motivation of this work, two desirable properties of surrogates
arise: (i) their capability to approximate the TBR MC model well and (ii) their
prediction time. An ideal surrogate would maximise
the former while minimising the latter.

@@

In some rows of~\cref{tbl:surrogates}, a single class in reality represents a
family of fundamentally similar approaches. Good examples of this are kriging methods and neural
networks. In the case of the former, multiple algorithms such as kriging based on
partial least squares and gradient-enhanced kriging are considered. In the
latter, a host of parametric graphs are defined to realise simplistic network
architecture search (see~\cref{fig:nn-archs} for details). Discrimination
between such options is considered an additional hyperparameter of the
corresponding surrogate class.

@@

The goal of the last two experiments is to exploit the information gathered by
hyperparameter tuning to investigate scaling properties. In
the third experiment, the 20~best-performing hyperparameter choices of each class
(in $R^2$) are used to learn surrogates using progressively larger training sets. Following
that, the fourth experiment aims to produce surrogates for practical use by
retraining selected well-scaling models to further optimise their properties.

>>>>

In the decoupled sampling approach that is further described
in~\cref{sec:supervised}, we first gather a sufficiently large
training set of samples $\mathcal{T}=\left\{\left( x^{(i)},f\left(x^{(i)}\right) \right)\right\}_{i=1}^N$
to describe the behaviour of $f(x)$ across its domain.
Depending on specific model family and appropriate choice of its
hyperparameters, surrogate models $\hat{f}(x)$ are trained to minimise
the empirical risk~$R_{\text{emp.}}$ with respect to $\mathcal{T}$ and a model-specific
loss function $\mathcal{L}$, where the empirical risk is defined as
$R_{\text{emp.}}(\hat{f}\mid\mathcal{T},\mathcal{L})
	=\frac{1}{N}\sum_{i=1}^N
	\mathcal{L}\left(\hat{f}(x^{(i)}),f(x^{(i)})\right)$.

@@

Aiming to provide objective comparison of a diverse set of surrogate model
families, we define a multitude of metrics to be tracked during experiments.
Following the motivation of this work, two desirable properties of surrogates
arise: (i) their capability to approximate the TBR MC model well and (ii) their
prediction time. An ideal surrogate would maximise
the former while minimising the latter.

@@

While some of the presented model families are clearly determined by an explicit
choice of a learning algorithm, others may vary considerably depending on
hyperparameter configuration. A good example of the latter group are artificial neural
networks, which in addition to conventional hyperparameters enable to control network
architecture through selection from various parametric graph templates
(see~\cref{fig:nn-archs} for details). This allows us to realise a simplistic
network architecture search during the hyperparameter optimisation procedure.

@@

The goal of the last two experiments is to exploit the information gathered by
hyperparameter tuning to investigate scaling properties. In
the third experiment, the 20~best-performing hyperparameter choices of each family
(in $R^2$) are used to learn surrogates using progressively larger training sets. Following
that, the fourth experiment aims to produce surrogates for practical use by
retraining selected well-scaling models to further optimise their properties.

### 2020-04-29 final_report/results.tex
replace model class with model family

We begin by evaluating a diverse set of surrogate classes that we proposed
earlier. In particular, we aim to study considered models in terms of regression
performance and prediction time.
Following~\cref{sec:experiment-methodology}, where we proposed four experiments
that accomplish this task, we present and discuss our results in the next
sections.

@@

The results displayed in~\cref{fig:exp1-time-vs-reg} indicate that in the first
experiment, gradient boosted trees clearly appear to be the most accurate as
well as the fastest surrogate class in terms of mean prediction time. Following
that, we note that extremely randomised trees, support vector machines and
artificial neural networks also achieved satisfactory results with respect to both examined metrics.
While the remainder of tested surrogate classes does not exhibit problems in
complexity, its regression performance falls below average.

\begin{figure}[h]
	\centering
	\begin{subfigure}[b]{0.333\textwidth}
		\centering
		\includegraphics[width=\linewidth]{exp1_slice0}
		\caption{Run 2, batches 0-3}
	\end{subfigure}\hfill%
	\begin{subfigure}[b]{0.333\textwidth}
		\centering
		\includegraphics[width=\linewidth]{exp1_slice1}
		\caption{Run 2, batches 100-103}
	\end{subfigure}\hfill%
	\begin{subfigure}[b]{0.333\textwidth}
		\centering
		\includegraphics[width=\linewidth]{exp1_slice2}
		\caption{Run 2, batches 200-203}
	\end{subfigure}
	\caption{20~best-performing surrogates per each considered class, plotted in
		terms of complexity (as $\overline{t}_{\text{pred.}}$) and regression
		performance (as~$R^2$) on selected slices of run~2, evaluated in
	experiment~1. Here, batches refer to subsets of training and test datasets that
	may be matched to slices using~\cref{tbl:slices}.}
	\label{fig:exp1-time-vs-reg}
\end{figure}

@@

% TODO: add tables here or in appendix with scaling results; for each metric
% create a table with rows = classes, columns = training set size, cells = mean +/- std
% it may be a lot, decide on placement and layout!

>>>>

We begin by evaluating a diverse set of surrogate families that we proposed
earlier. In particular, we aim to study considered models in terms of regression
performance and prediction time.
Following~\cref{sec:experiment-methodology}, where we proposed four experiments
that accomplish this task, we present and discuss our results in the next
sections.

@@

The results displayed in~\cref{fig:exp1-time-vs-reg} indicate that in the first
experiment, gradient boosted trees clearly appear to be the most accurate as
well as the fastest surrogate family in terms of mean prediction time. Following
that, we note that extremely randomised trees, support vector machines and
artificial neural networks also achieved satisfactory results with respect to both examined metrics.
While the remainder of tested surrogate families does not exhibit problems in
complexity, its regression performance falls below average.

\begin{figure}[h]
	\centering
	\begin{subfigure}[b]{0.333\textwidth}
		\centering
		\includegraphics[width=\linewidth]{exp1_slice0}
		\caption{Run 2, batches 0-3}
	\end{subfigure}\hfill%
	\begin{subfigure}[b]{0.333\textwidth}
		\centering
		\includegraphics[width=\linewidth]{exp1_slice1}
		\caption{Run 2, batches 100-103}
	\end{subfigure}\hfill%
	\begin{subfigure}[b]{0.333\textwidth}
		\centering
		\includegraphics[width=\linewidth]{exp1_slice2}
		\caption{Run 2, batches 200-203}
	\end{subfigure}
	\caption{20~best-performing surrogates per each considered family, plotted in
		terms of complexity (as $\overline{t}_{\text{pred.}}$) and regression
		performance (as~$R^2$) on selected slices of run~2, evaluated in
	experiment~1. Here, batches refer to subsets of training and test datasets that
	may be matched to slices using~\cref{tbl:slices}.}
	\label{fig:exp1-time-vs-reg}
\end{figure}

@@

### 2020-04-29 final_report/tbr_final_report-metadata.tex
replace model class with model family

% Abstract - % directly after { is important for correct indentation
\DISAbstract{%
 The tritium breeding ratio (TBR) is an essential quantity for the design of
 modern and next-generation Tokamak nuclear fusion reactors. Representing the
 ratio between tritium fuel generated in breeding blankets at the boundary of
 the reactor, and fuel consumed during reactor runtime, the TBR depends in a
 complex manner on reactor geometry and material properties. We explored the
 training of surrogate models to produce a cheap but high-quality approximation
 for a Monte Carlo TBR model in use at the UK Atomic Energy Authority. We
 investigated possibilities for dimensional reduction on the parameter space of
 this model, and reviewed $N$ classes of surrogate models for potential % TODO
 applicability. Here we present the performance and scaling properties of these
 surrogate models, the best of which demonstrated an accuracy of $X$ and a mean % TODO
 prediction time of $X$, representing a relative speedup $X$ with respect to the % TODO
 MC model. We further present a novel adaptive sampling algorithm, QASS, capable
 of interfacing with any of the individual studied models. Our preliminary
 testing on a toy TBR theory has demonstrated the efficacy of this algorithm for
 speeding up the surrogate modelling process.
}

>>>>

% Abstract - % directly after { is important for correct indentation
\DISAbstract{%
 The tritium breeding ratio (TBR) is an essential quantity for the design of
 modern and next-generation Tokamak nuclear fusion reactors. Representing the
 ratio between tritium fuel generated in breeding blankets at the boundary of
 the reactor, and fuel consumed during reactor runtime, the TBR depends in a
 complex manner on reactor geometry and material properties. We explored the
 training of surrogate models to produce a cheap but high-quality approximation
 for a Monte Carlo TBR model in use at the UK Atomic Energy Authority. We
 investigated possibilities for dimensional reduction on the parameter space of
 this model, and reviewed $N$ families of surrogate models for potential % TODO
 applicability. Here we present the performance and scaling properties of these
 surrogate models, the best of which demonstrated an accuracy of $X$ and a mean % TODO
 prediction time of $X$, representing a relative speedup $X$ with respect to the % TODO
 MC model. We further present a novel adaptive sampling algorithm, QASS, capable
 of interfacing with any of the individual studied models. Our preliminary
 testing on a toy TBR theory has demonstrated the efficacy of this algorithm for
 speeding up the surrogate modelling process.
}
